---
title: "Dynamic Report"
author: "Korede Adegboye"
header-includes:
  - \usepackage{pdfpages}
params:
  p1: NA
  p2: NA
  p3: NA
  p4: NA
  dfnew: NA
  count: NA
---

# Showcasing the strongest evidence for climate change
### Temperature Trends
Extreme values, as cautionary bounds
February and July
Minimum and Maximum
Highlights
Temperature slopes vary within Canada, provinces and cities
Majority of Canada is in fact, experiencing increasing temperatures
Nunavut and the Northwest Territories - North Region temperatures increase at a faster rate than the southern regions
December through February warm faster than the other months
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Results 
```{r kxpand, echo= FALSE, results = 'asis'}
library(knitr)
kexpand <- function(plot) {

    c(knit_child(
        text=(
"```{r child, results = 'asis', echo = FALSE}
grid.draw(plot) 
```"),
      quiet  = TRUE
  ))
}
```

```{r for_loop, echo=FALSE, results = 'asis'}
  # L <- htmltools::tagList()
  # L[[1]] <- grid.draw(params$dfnew[[1]])
  # L[[2]] <- grid.draw(params$dfnew[[2]])

  L <- htmltools::tagList()

for(i in 1:length(params$dfnew)){
  # print(length(params$dfnew))
  # kexpand(params$dfnew[[i]])
  L[[i]] <- invisible(params$dfnew[[i]])
  # htmltools:tagList(i)
  kexpand(L[[i]])

}

```

